### 2021-12-17 documents/floats/comepara.tex
a thousand small fixes
small fixes

\begin{table}[h]
\centering
\caption[\rc{ət-epɨ} \qu{to come} in paradigms]{\rc{ət-epɨ} \qu{to come} in paradigms \parencites[113, 150, 153, 156]{alves2017arara}[294; p.c., Spike Gildea]{triomeira1999}}
\label{tab:comepara}
\begin{tabular}[t]{@{}llll@{}}
\mytoprule
{} &          \kaxui &          \arara &          \trio \\
\mymidrule
\gl{1}   &   \obj{w-oohɨ-} &    \obj{w-ebɨ-} &  \obj{w-əepɨ-} \\
\gl{2}   &   \obj{m-oohɨ-} &  \obj{m-odebɨ-} &  \obj{mən-epɨ} \\
\gl{1+2} &  \obj{kɨs-ohɨ-} &  \obj{kud-ebɨ-} &   \obj{ke-epɨ} \\
\gl{3}   &    \obj{n-ehɨ-} &    \obj{t-ebɨ-} &    \obj{n-epɨ} \\
\mybottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\centering
\caption[\rc{(ət-)epɨ} \qu{to come} in paradigms]{\rc{(ət-)epɨ} \qu{to come} in paradigms \parencites[113, 150, 153, 156]{alves2017arara}[294; p.c., Spike Gildea]{triomeira1999}}
\label{tab:comepara}
\begin{tabular}[t]{@{}llll@{}}
\mytoprule
{} &          \kaxui &          \arara &          \trio \\
\mymidrule
\gl{1}   &   \obj{w-oohɨ-} &    \obj{w-ebɨ-} &  \obj{w-əepɨ-} \\
\gl{2}   &   \obj{m-oohɨ-} &  \obj{m-odebɨ-} &  \obj{mən-epɨ} \\
\gl{1+2} &  \obj{kɨs-ohɨ-} &  \obj{kud-ebɨ-} &   \obj{ke-epɨ} \\
\gl{3}   &    \obj{n-ehɨ-} &    \obj{t-ebɨ-} &    \obj{n-epɨ} \\
\mybottomrule
\end{tabular}
\end{table}

### 2021-12-17 documents/floats/participles.tex
regular verbs in data and docs
moved verb discussion to verbs section, fixed lingpy alignments, fixed map
rewriting and restructuring
a thousand small fixes
small fixes

\begin{tabular}[t]{@{}lll@{}}
\toprule
Language &                               \gl{s_a_} &                        \gl{s_p_} \\
\midrule
\kaxui  &         \obj{t-ehurka-t͡ʃe} \qu{fallen} &       \obj{tɨ-jaʔ-so} \qu{burnt} \\
\arara  &         \obj{t-\emp{o-}ep-te} \qu{come} &      \obj{t-oregrum-te} \qu{sad} \\
\trio   &    \obj{tɨ-\emp{w-}əturu-e} \qu{talked} &       \obj{t-əpəə-se} \qu{tired} \\
\wayana &     \obj{tə-\emp{w-}epɨ-he} \qu{bathed} &    \obj{t-onopɨ-he} \qu{painted} \\
\apalai &  \obj{t-\emp{o-}erama-se} \qu{returned} &      \obj{t-anorɨ-se} \qu{dried} \\
\kalina &  \obj{tu-\emp{w-}oʔka-se} \qu{come out} &       \obj{t-okari-se} \qu{told} \\
\panare &  \obj{t-\emp{o-}tatɨhpə-se} \qu{wailed} &  \obj{tɨ-sɨrɨke-t͡ʃe} \qu{tired} \\
\bottomrule
\end{tabular}

>>>>

\begin{table}
\centering
\caption[Participles of \gl{s_a_} and \gl{s_p_} verbs]{Participles of \gl{s_a_} and \gl{s_p_} verbs \parencites[39]{schuring2018kaxuyana}[118, 207]{alves2017arara}[333-334]{triomeira1999}[400]{wayanatavares2005}[35]{koehn1986apalai}[kuruaz-154]{koehns1994textos}[430, 433]{hoff1968carib}[232, 244]{panarepayne2013}}
\label{tab:participles}
\begin{tabular}[t]{@{}lll@{}}
\mytoprule
Language &                               \gl{s_a_} &                        \gl{s_p_} \\
\mymidrule
\kaxui  &         \obj{t-ehurka-t͡ʃe} \qu{fallen} &       \obj{tɨ-jaʔ-so} \qu{burnt} \\
\arara  &         \obj{t-\emp{o-}ep-te} \qu{come} &      \obj{t-oregrum-te} \qu{sad} \\
\trio   &    \obj{tɨ-\emp{w-}əturu-e} \qu{talked} &       \obj{t-əpəə-se} \qu{tired} \\
\wayana &     \obj{tə-\emp{w-}epɨ-he} \qu{bathed} &    \obj{t-onopɨ-he} \qu{painted} \\
\apalai &        \obj{t-\emp{o-}ɨto-se} \qu{gone} &   \obj{t-ɨhto-se} \qu{gone down} \\
\kalina &  \obj{tu-\emp{w-}oʔka-se} \qu{come out} &       \obj{t-okari-se} \qu{told} \\
\panare &  \obj{t-\emp{o-}tatɨhpə-se} \qu{wailed} &  \obj{tɨ-sɨrɨke-t͡ʃe} \qu{tired} \\
\mybottomrule
\end{tabular}
\end{table}

### 2021-12-17 documents/floats/ppekverbs.tex
a thousand small fixes
small fixes

\begin{table}[h]
\centering
\caption[Verbs preserving \gl{1}\gl{s_a_} \rc{w-} in \PPek]{Verbs preserving \gl{1}\gl{s_a_} \rc{w-} in \PPek \parencites[153, 200]{alves2017arara}[42, 80, 139, 209]{ikpengpacheco2001}[76, 130, 131, 374, 397]{von1892bakairi}[68]{ikpengpacheco1997}[4]{meira2003bakairi}}
\label{tab:ppekverbs}
\begin{tabular}[t]{@{}lllll@{}}
\mytoprule
{} &          \PPek &          \arara &                       \ikpeng &        \bakairi \\
\mymidrule
\qu{say}     &    \rc{wɨ-ge-} &    \obj{wɨ-ge-} &                   \obj{ɨ-ge-} &     \obj{u-ge-} \\
\qu{go}      &   \rc{w-ɨtən-} &    \obj{w-ɨdo-} &                 \obj{k-aran-} &     \obj{u-tə-} \\
\qu{be-1}    &     \rc{w-ap-} &     \obj{w-ap-} &                             – &      \obj{w-a-} \\
\qu{be-2}    &  \rc{w-et͡ʃi-} &  \obj{w-it͡ʃi-} &  \obj{{\normalfont ∅}-et͡ʃi-} &      \obj{w-i-} \\
\qu{come}    &    \rc{w-epɨ-} &    \obj{w-ebɨ-} &                 \obj{k-arep-} &   \obj{k-əewɨ-} \\
\qu{go down} &   \rc{w-ɨptə-} &  \obj{w-iptoŋ-} &  \obj{{\normalfont ?}-iptoŋ-} &  \obj{k-ɨtəgɨ-} \\
\qu{bathe}   &    \rc{w-ipɨ-} &    \obj{w-ibɨ-} &     \obj{{\normalfont ∅}-ip-} &      \obj{w-i-} \\
\mybottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\centering
\caption[Verbs preserving \gl{1}\gl{s_a_} \rc{w-} in \PPek]{Verbs preserving \gl{1}\gl{s_a_} \rc{w-} in \PPek \parencites[153, 200]{alves2017arara}[42, 80, 139, 209]{ikpengpacheco2001}[76, 130-131, 374, 397]{von1892bakairi}[68]{ikpengpacheco1997}[4]{meira2003bakairi}}
\label{tab:ppekverbs}
\begin{tabular}[t]{@{}lllll@{}}
\mytoprule
{} &          \PPek &          \arara &                       \ikpeng &        \bakairi \\
\mymidrule
\qu{say}     &    \rc{wɨ-ge-} &    \obj{wɨ-ge-} &                   \obj{ɨ-ge-} &     \obj{u-ge-} \\
\qu{go}      &   \rc{w-ɨtən-} &    \obj{w-ɨdo-} &                 \obj{k-aran-} &     \obj{u-tə-} \\
\qu{be-1}    &     \rc{w-ap-} &     \obj{w-ap-} &                             – &      \obj{w-a-} \\
\qu{be-2}    &  \rc{w-et͡ʃi-} &  \obj{w-it͡ʃi-} &  \obj{{\normalfont ∅}-et͡ʃi-} &      \obj{w-i-} \\
\qu{come}    &    \rc{w-epɨ-} &    \obj{w-ebɨ-} &                 \obj{k-arep-} &   \obj{k-əewɨ-} \\
\qu{go down} &   \rc{w-ɨptə-} &  \obj{w-iptoŋ-} &  \obj{{\normalfont ?}-iptoŋ-} &  \obj{k-ɨtəgɨ-} \\
\qu{bathe}   &    \rc{w-ipɨ-} &    \obj{w-ibɨ-} &     \obj{{\normalfont ∅}-ip-} &      \obj{w-i-} \\
\mybottomrule
\end{tabular}
\end{table}

### 2021-12-17 documents/floats/ptirverbs.tex
new approach to testing predictions from bybee's model
moved verb discussion to verbs section, fixed lingpy alignments, fixed map
rewriting and restructuring
more trimming, fixed verb citations
changed reconstruction of 'to come'
a thousand small fixes
small fixes

\begin{table}
\centering
\caption[Verbs preserving \gl{1}\gl{s_a_} \rc{w-} in \PTir]{Verbs preserving \gl{1}\gl{s_a_} \rc{w-} in \PTir \parencites[112, 113, 114, 115, 165]{meira1998proto}[292, 294, 339]{triomeira1999}}
\label{tab:ptirverbs}
\begin{tabular}[t]{@{}llll@{}}
\mytoprule
{} &          \PTir &          \trio &                     \akuriyo \\
\midrule
\qu{be-1} &      \rc{w-a-} &     \obj{w-a-} &     \obj{{\normalfont ∅}-a-} \\
\qu{be-2} &    \rc{w-eʔi-} &    \obj{w-ei-} &   \obj{{\normalfont ?}-eʔi-} \\
\qu{say}  &    \rc{wɨ-ka-} &   \obj{wɨ-ka-} &                 \obj{wɨ-ka-} \\
\qu{go}   &  \rc{wɨ-təmɨ-} &  \obj{wɨ-tən-} &                \obj{ə-təmɨ-} \\
\qu{come} &  \rc{w-əʔepɨ-} &  \obj{w-əepɨ-} &  \obj{{\normalfont ∅}-eepɨ-} \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\centering
\caption[Verbs preserving \gl{1}\gl{s_a_} \rc{w-} in \PTir]{Verbs preserving \gl{1}\gl{s_a_} \rc{w-} in \PTir \parencites[292, 294, 339]{triomeira1999}[112-115, 165]{meira1998proto}}
\label{tab:ptirverbs}
\begin{tabular}[t]{@{}llll@{}}
\mytoprule
{} &          \PTir &          \trio &                     \akuriyo \\
\mymidrule
\qu{say}  &    \rc{wɨ-ka-} &   \obj{wɨ-ka-} &                 \obj{wɨ-ka-} \\
\qu{go}   &  \rc{w-ɨtəmɨ-} &  \obj{wɨ-tən-} &                \obj{ə-təmɨ-} \\
\qu{be-1} &      \rc{w-a-} &     \obj{w-a-} &     \obj{{\normalfont ∅}-a-} \\
\qu{be-2} &    \rc{w-eʔi-} &    \obj{w-ei-} &   \obj{{\normalfont ?}-eʔi-} \\
\qu{come} &  \rc{w-əʔepɨ-} &  \obj{w-əepɨ-} &  \obj{{\normalfont ∅}-eepɨ-} \\
\mybottomrule
\end{tabular}
\end{table}

### 2021-12-17 documents/floats/pwaireg.tex
small fixes

\begin{table}
\centering
\caption[Regular \PWai verbs]{Regular \qu{to fall} (\gl{s_a_}) and \qu{to sleep} (\gl{s_p_}) in \PWai \parencites[150]{howard2001wrought}[209, 211]{hawkins1953waiwai}[189, 190, 196]{hixkaryanaderby1985}[30]{waiwaihawkins1998}}
\label{tab:pwaireg}
\begin{tabular}[t]{@{}lllllll@{}}
\mytoprule
{} &     \qu{to fall} &                  &                    &      \qu{to sleep} &                 &                    \\
{} &            \PWai &           \hixka &            \waiwai &              \PWai &          \hixka &            \waiwai \\
\mymidrule
\gl{1}   &  \obj{k-eɸurka-} &  \obj{k-ehurka-} &    \obj{k-eɸɨrka-} &   \obj{kɨ-wɨnɨkɨ-} &  \obj{kɨ-nɨkɨ-} &   \obj{kɨ-wɨnɨkɨ-} \\
\gl{2}   &  \obj{m-eɸurka-} &  \obj{m-ehurka-} &    \obj{m-eɸɨrka-} &    \obj{o-wɨnɨkɨ-} &  \obj{o-wnɨkɨ-} &   \obj{mɨ-wɨnɨkɨ-} \\
\gl{1+2} &  \obj{t-eɸurka-} &  \obj{t-ehurka-} &  \obj{t͡ʃ-eɸɨrka-} &  \obj{tɨt-wɨnɨkɨ-} &  \obj{tɨ-nɨkɨ-} &  \obj{tɨt-wɨnɨkɨ-} \\
\gl{3}   &  \obj{ɲ-eɸurka-} &  \obj{ɲ-ehurka-} &    \obj{ɲ-eɸɨrka-} &   \obj{nɨ-wɨnɨkɨ-} &  \obj{nɨ-nɨkɨ-} &   \obj{nɨ-wɨnɨkɨ-} \\
\mybottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\centering
\caption[Regular \PWai verbs]{Regular \qu{to fall} (\gl{s_a_}) and \qu{to sleep} (\gl{s_p_}) in \PWai \parencites[189-190, 196]{hixkaryanaderby1985}[209, 211]{hawkins1953waiwai}[150]{howard2001wrought}[30]{waiwaihawkins1998}}
\label{tab:pwaireg}
\begin{tabular}[t]{@{}lllllll@{}}
\mytoprule
{} &     \qu{to fall} &                  &                    &      \qu{to sleep} &                 &                    \\
{} &            \PWai &           \hixka &            \waiwai &              \PWai &          \hixka &            \waiwai \\
\mymidrule
\gl{1}   &  \obj{k-eɸurka-} &  \obj{k-ehurka-} &    \obj{k-eɸɨrka-} &   \obj{kɨ-wɨnɨkɨ-} &  \obj{kɨ-nɨkɨ-} &   \obj{kɨ-wɨnɨkɨ-} \\
\gl{2}   &  \obj{m-eɸurka-} &  \obj{m-ehurka-} &    \obj{m-eɸɨrka-} &    \obj{o-wɨnɨkɨ-} &  \obj{o-wnɨkɨ-} &   \obj{mɨ-wɨnɨkɨ-} \\
\gl{1+2} &  \obj{t-eɸurka-} &  \obj{t-ehurka-} &  \obj{t͡ʃ-eɸɨrka-} &  \obj{tɨt-wɨnɨkɨ-} &  \obj{tɨ-nɨkɨ-} &  \obj{tɨt-wɨnɨkɨ-} \\
\gl{3}   &  \obj{ɲ-eɸurka-} &  \obj{ɲ-ehurka-} &    \obj{ɲ-eɸɨrka-} &   \obj{nɨ-wɨnɨkɨ-} &  \obj{nɨ-nɨkɨ-} &   \obj{nɨ-wɨnɨkɨ-} \\
\mybottomrule
\end{tabular}
\end{table}

### 2021-12-17 documents/floats/pwaiverbs.tex
new approach to testing predictions from bybee's model
moved verb discussion to verbs section, fixed lingpy alignments, fixed map
rewriting and restructuring
more trimming, fixed verb citations
a thousand small fixes
small fixes

\begin{table}
\centering
\caption[Verbs preserving \gl{1}\gl{s_a_} \rc{w-} in \PWai]{Verbs preserving \gl{1}\gl{s_a_} \rc{w-} in \PWai \parencites[70, 197, 198]{hixkaryanaderby1985}[4]{hixkaryanaderby1979}[71, 85; p.c., Spike Gildea]{waiwaihawkins1998}}
\label{tab:pwaiverbs}
\begin{tabular}[t]{@{}llll@{}}
\mytoprule
{} &         \PWai &        \hixka &         \waiwai \\
\midrule
\qu{be-1} &    \rc{w-ah-} &   \obj{w-ah-} &      \obj{w-a-} \\
\qu{be-2} &   \rc{w-eʃi-} &  \obj{w-eʃe-} &   \obj{w-eeʃi-} \\
\qu{say}  &   \rc{wɨ-ka-} &   \obj{ɨ-ka-} &    \obj{wɨ-ka-} \\
\qu{go}   &  \rc{wɨ-tom-} &   \obj{ɨ-to-} &  \obj{kɨw-tom-} \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\centering
\caption[Verbs preserving \gl{1}\gl{s_a_} \rc{w-} in \PWai]{Verbs preserving \gl{1}\gl{s_a_} \rc{w-} in \PWai \parencites[4]{hixkaryanaderby1979}[71, 85]{waiwaihawkins1998}[70, 197-198; p.c., Spike Gildea]{hixkaryanaderby1985}}
\label{tab:pwaiverbs}
\begin{tabular}[t]{@{}llll@{}}
\mytoprule
{} &         \PWai &        \hixka &         \waiwai \\
\mymidrule
\qu{say}  &   \rc{wɨ-ka-} &   \obj{ɨ-ka-} &    \obj{wɨ-ka-} \\
\qu{go}   &  \rc{wɨ-tom-} &   \obj{ɨ-to-} &  \obj{kɨw-tom-} \\
\qu{be-1} &    \rc{w-ah-} &   \obj{w-ah-} &      \obj{w-a-} \\
\qu{be-2} &   \rc{w-eʃi-} &  \obj{w-eʃe-} &   \obj{w-eeʃi-} \\
\mybottomrule
\end{tabular}
\end{table}

### 2021-12-17 documents/floats/say.tex
changed reconstruction of 'to come'
a thousand small fixes
small fixes

\begin{table}[h]
\centering
\caption[Reflexes of \rc{ka[ti]} \qu{to say}]{Reflexes of \rc{ka[ti]} \qu{to say} \parencites[267]{meira2005bakairi}[4]{meira2003bakairi}[48]{franchetto2008absolutivo}[209, 209, 279]{ikpengpacheco2001}[80, 153]{alves2017arara}[182]{hixkaryanaderby1985}[113]{meira1998proto}[107]{koehn1986apalai}[26]{waiwaihawkins1998}[66]{camargo2010wayana}[59]{macushiabbott1991}[123]{swiggers2010gramatica}[430]{courtz2008carib}[125]{akawaiocaesar2003}[102]{mattei1994diccionario}[63; p.c., Spike Gildea]{largo2011yukpa}}
\label{tab:say}
\begin{tabular}[t]{@{}llllll@{}}
\mytoprule
Language &          Form &    &    &    &    \\
\mymidrule
\kaxui   &   \obj{ka[s]} &  k &  a &  s &    \\
\PWai    &    \rc{ka[s]} &  k &  a &  s &    \\
\hixka   &   \obj{ka[s]} &  k &  a &  s &    \\
\waiwai  &   \obj{ka[s]} &  k &  a &  s &    \\
\PPek    &       \rc{ge} &  g &  e &    &    \\
\PPek    &       \rc{ke} &  k &  e &    &    \\
\arara   &      \obj{ge} &  g &  e &    &    \\
\arara   &      \obj{ke} &  k &  e &    &    \\
\ikpeng  &      \obj{ge} &  g &  e &    &    \\
\ikpeng  &    \obj{k[e]} &  k &  e &    &    \\
\bakairi &      \obj{ke} &  k &  e &    &    \\
\bakairi &      \obj{ge} &  g &  e &    &    \\
\PTir    &       \rc{ka} &  k &  a &    &    \\
\trio    &      \obj{ka} &  k &  a &    &    \\
\akuriyo &      \obj{ka} &  k &  a &    &    \\
\carijo  &      \obj{ka} &  k &  a &    &    \\
\wayana  &   \obj{ka[i]} &  k &  a &    &  i \\
\apalai  &  \obj{ka[ʃi]} &  k &  a &  ʃ &  i \\
\kalina  &      \obj{ka} &  k &  a &    &    \\
\kapon   &      \obj{ka} &  k &  a &    &    \\
\pemon   &      \obj{ka} &  k &  a &    &    \\
\macushi &      \obj{ka} &  k &  a &    &    \\
\panare  &   \obj{ka[h]} &  k &  a &  h &    \\
\uxc     &      \obj{ki} &  k &  i &    &    \\
\yukpa   &      \obj{ka} &  k &  a &    &    \\
\mybottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\centering
\caption[Reflexes of \rc{ka[ti]} \qu{to say}]{Reflexes of \rc{ka[ti]} \qu{to say} \parencites[267]{meira2005bakairi}[4]{meira2003bakairi}[48]{franchetto2008absolutivo}[209, 279]{ikpengpacheco2001}[80, 153]{alves2017arara}[182]{hixkaryanaderby1985}[113]{meira1998proto}[107]{koehn1986apalai}[26]{waiwaihawkins1998}[66]{camargo2010wayana}[59]{macushiabbott1991}[123]{swiggers2010gramatica}[430]{courtz2008carib}[125]{akawaiocaesar2003}[102]{mattei1994diccionario}[63; p.c., Spike Gildea]{largo2011yukpa}}
\label{tab:say}
\begin{tabular}[t]{@{}llllll@{}}
\mytoprule
Language &          Form &    &    &    &    \\
\mymidrule
\kaxui   &   \obj{ka[s]} &  k &  a &  s &    \\
\PWai    &    \rc{ka[s]} &  k &  a &  s &    \\
\hixka   &   \obj{ka[s]} &  k &  a &  s &    \\
\waiwai  &   \obj{ka[s]} &  k &  a &  s &    \\
\PPek    &       \rc{ge} &  g &  e &    &    \\
\PPek    &       \rc{ke} &  k &  e &    &    \\
\arara   &      \obj{ge} &  g &  e &    &    \\
\arara   &      \obj{ke} &  k &  e &    &    \\
\ikpeng  &      \obj{ge} &  g &  e &    &    \\
\ikpeng  &    \obj{k[e]} &  k &  e &    &    \\
\bakairi &      \obj{ge} &  g &  e &    &    \\
\bakairi &      \obj{ke} &  k &  e &    &    \\
\PTir    &       \rc{ka} &  k &  a &    &    \\
\trio    &      \obj{ka} &  k &  a &    &    \\
\akuriyo &      \obj{ka} &  k &  a &    &    \\
\carijo  &      \obj{ka} &  k &  a &    &    \\
\wayana  &   \obj{ka[i]} &  k &  a &    &  i \\
\apalai  &  \obj{ka[ʃi]} &  k &  a &  ʃ &  i \\
\kalina  &      \obj{ka} &  k &  a &    &    \\
\kapon   &      \obj{ka} &  k &  a &    &    \\
\pemon   &      \obj{ka} &  k &  a &    &    \\
\macushi &      \obj{ka} &  k &  a &    &    \\
\panare  &   \obj{ka[h]} &  k &  a &  h &    \\
\uxc     &      \obj{ki} &  k &  i &    &    \\
\yukpa   &      \obj{ka} &  k &  a &    &    \\
\mybottomrule
\end{tabular}
\end{table}
